Bibliometrics

### 2024-12-30 data-raw/01-bibliometrics-analysis.qmd
some updates to the manuscript

Plot:
```{r}
ggplot(data = layout) +
  geom_point(aes(x = x,
                 y = y,
                 shape = corpus,
                 color = corpus),
             size = 3,
             alpha = 0.7) +
  geom_point(data = layout |>
               filter(corpus == "Both"),
             aes(x = x,
                 y = y),
             shape = 1,
             size = 3) +
  geom_point(data = layout |>
               filter(corpus == "Wilson"),
             aes(x = x,
                 y = y),
             shape = 0,
             size = 3,
             alpha = 0.5) +

  theme_void()
```

@@

Who are the authors in that niche that cites both Wilson and Hansen, and what is the temporal pattern of publication?
```{r}
corpus |> 
  filter(corpus == "Both") |> 
  select(AU, PY) |> arrange(PY)
```

>>>>

Plot:
```{r}
ggplot(data = layout) +
  geom_point(aes(x = x,
                 y = y,
                 shape = corpus,
                 color = corpus),
             size = 3,
             alpha = 0.7) +
  geom_point(data = layout |>
               filter(corpus == "Both"),
             aes(x = x,
                 y = y),
             shape = 1,
             size = 3) +
  geom_point(data = layout |>
               filter(corpus == "Wilson"),
             aes(x = x,
                 y = y),
             shape = 0,
             size = 3,
             alpha = 0.5) +
  theme_void()
ggsave("Han_Wilson_bib_coupling_plot.png")
```

@@

Who are the authors in that niche that cites both Wilson and Hansen, and what is the temporal pattern of publication?
```{r}
both_Han_Wilson <- 
  corpus |> 
  filter(corpus == "Both") |> 
  select(AU, PY, TI) |> arrange(PY)

write.csv(both_Han_Wilson, file = "both_Han_Wilson.csv")
```
